---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggreach

<!-- badges: start -->
<!-- badges: end -->

The goal of ggreach is to facilitate custom REACH-themed plotting and palette functions that integrate into ggplot figures

## Installation



You can download the latest development version of the package on [GitHub](https://github.com/) with:

``` {r, eval=F}
# install.packages("devtools")
devtools::install_github("zackarno/ggreach")
```
## Example

```{r example, message = FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(ggreach)
## basic example code
```

### Discrete color scale

Using the iris data set we can do a simple geom point plot and add the scale_reach_color argument. The default setting is discrete colors

```{r discrete_color}
iris %>% 
  ggplot(aes(x=Sepal.Length,y=Sepal.Width, color=Species))+
  geom_point()+
  scale_color_reach()+
  theme_bw()
```

Often when assessment data is crunched (via butteR or HypegrammaR) the results are a long format data set. These long format datasets are also very easily piped into ggplot. The **scale_fill_reach** function will fill barplot with REACH-palette colors

```{r assessment_results_discrete}
assessment_results %>% 
  filter(variable=="i.income_cat") %>% 
  ggplot(aes(x=variable_val,y=`mean/pct`, fill=subset_1_val))+
  geom_bar(stat="identity",position=position_dodge(width=0.9))+
  coord_flip()+
  scale_fill_reach()+
  theme_bw()+
  theme(
    legend.title = element_blank()
  )

```

### Continuous color scale
To get a continuous color scale  you need to specify discrete as F and specify a REACH palette you want to use.
```{r continuous color}
iris %>% 
  ggplot(aes(x=Sepal.Length,y=Sepal.Width, color=Sepal.Width))+
  geom_point()+
  scale_color_reach(palette = "reds",discrete = F)+
  theme_bw()
```

There are now multiple singleband palettes

```{r}
iris %>% 
  ggplot(aes(x=Sepal.Length,y=Sepal.Width, color=Sepal.Width))+
  geom_point()+
  scale_color_reach(palette = "lightgreens",discrete = F)+
  theme_bw()
```

Currently there are about 12 singleband color palettes based on the REACH Graphic Charter and just 2 categorical palettes available (`classic', 'classic_extended'). However, we will be integrating more categorical and dual & tri-color ramps.
