---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggreach

<!-- badges: start -->
<!-- badges: end -->

The goal of ggreach is to facilitate custom REACH-themed plotting and palette functions that integrate into ggplot figures

## Installation



You can download the latest development version of the package on [GitHub](https://github.com/) with:

``` {r, eval=F}
# install.packages("devtools")
devtools::install_github("zackarno/ggreach")
```
## Example

```{r example, message = FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(ggreach)
## basic example code
```

### Discrete color scale

Using the iris data set we can do a simple geom point plot and add the scale_reach_color argument. The default setting is discrete colors

```{r discrete_color}
iris %>% 
  ggplot(aes(x=Sepal.Length,y=Sepal.Width, color=Species))+
  geom_point()+
  scale_color_reach()+
  theme_bw()
```

### Continuous color scale
To get a continuous color scale  you need to specify discrete as F and specify a REACH palette you want to use
```{r continuous color}
iris %>% 
  ggplot(aes(x=Sepal.Length,y=Sepal.Width, color=Sepal.Width))+
  geom_point()+
  scale_color_reach(palette = "reds",discrete = F)+
  theme_bw()
```

Currently only the following palettes are available : 'main'(categorical), 'reds', 'greys', 'beiges'. However we will soon be integrate 2 and three color continuous color scales which will the colorbrewer naming convention (i.e GrRd, YlGrRd)
